Depression and suicidality as costly signals of need

### 2021-03-21 Paper.rmd
Added Division effects plots

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
library(equatiomatic)
library(knitr)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(hagenutils)

@@

```{r mediation, fig.height=4, fig.cap="The effect of Depression (treatment) vs. Verbal request (control) on Action is largely mediated by Belief. ACME: Average causal mediation effect. ADE: Average direct effect. The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action. Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
ggmediation(med1b)
```

@@

@@

```{r t2action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action."}
effectsPlots$m26plot
```

>>>>

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
# options(warn = 2)
library(equatiomatic)
library(knitr)
library(kableExtra)
library(ggplot2)
library(patchwork)
library(hagenutils)

@@

```{r mediation, fig.height=4, fig.cap="The effect of Depression (treatment) vs. Verbal request (control) on Action (0-1 scale) is largely mediated by Belief. ACME: Average causal mediation effect. ADE: Average direct effect. The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action. Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
ggmediation(med1b)
```

@@

## The effect of signals on T2 division in thwarted marriage vignette

```{r division, fig.width=9, fig.cap="Effect of signals on division of dowry between the daughters in the thwarted marriage vignette, with an interaction between T1 Division and signal. Means estimated with a generalized linear regression model with the quasibinomial family."}
effectsPlots$m7
```

```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on T2 Division of dowry between the daughters in the thwarted marriage vignette."}
effectsPlots$m8
```

@@

```{r t2action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action."}
effectsPlots$m26plot + theme(panel.spacing = unit(1.5, "lines"))
```
